ms_5

### 2020-04-26 ms_5.Rmd
fixing col spec
fixed col spec except for death by year and state

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv", 
                                    col_types = "lcdccddddddddic")

@@

treatment_locations <- read_csv("Drug Treatment Centers.csv") %>%
  select(`Program Name`, Street, City, State, Zipcode)

@@

state_pop <- read_csv("State Population Estimate.csv") %>%
  rename(state_full = NAME) %>%
  mutate(state_full = tolower(state_full))

@@

longlatinfo <- read_csv("uscitieslonglat.csv") %>%
  rename(City = city) %>%
  rename(State = state_id)

@@

madeathbyagegender <- read_csv("MAFatalOpioidOverdosesByAgeAndGender.csv")

macountyheroin <- read_csv("MAHeroinAsPrimarySubstanceOfUse.csv")

madeathbyrace <- read_csv("MAOpioidDeathsByRaceAndEthnicity.csv")

matypeofsubstance <- read_csv("MAPrimarySubstanceofUseWhenEnteringTreatmentbyTown.csv")

toxdeath <- read_csv("MAProportionDecedentsWithRxHistorybyToxicologyScreen.csv",
         skip = 1)

@@

```{r}
counties <- read_csv("zip_codes_states.csv") %>%
  filter(state == "MA") %>%
  rename(County = county) %>%
  rename(Municipality = city)

madeathbycounty <- read_csv("MAAverageAnnualOpioidRelatedDeathRateper100,000People.csv")

countypop <- read_csv("countypop.csv") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)

@@

povertybycounty <- read_csv("PovertyByCounty.csv") %>%
  rename(subregion = County) %>%
  mutate(subregion = tolower(subregion))

>>>>

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv", 
                                    col_types = "lcdccddddc")

@@

treatment_locations <- read_csv("Drug Treatment Centers.csv", col_types = "ccccccccc") %>%
  select(`Program Name`, Street, City, State, Zipcode)

@@

state_pop <- read_csv("State Population Estimate.csv", col_types = "dccdcdddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd") %>%
  rename(state_full = NAME) %>%
  mutate(state_full = tolower(state_full))

@@

longlatinfo <- read_csv("uscitieslonglat.csv", col_types = "ccccdcccddddcllcdcd") %>%
  rename(City = city) %>%
  rename(State = state_id)

@@

madeathbyagegender <- read_csv("MAFatalOpioidOverdosesByAgeAndGender.csv",
                               col_types = "ccddd")

macountyheroin <- read_csv("MAHeroinAsPrimarySubstanceOfUse.csv",
                           col_types = "ccccc")

madeathbyrace <- read_csv("MAOpioidDeathsByRaceAndEthnicity.csv",
                          col_types = "dcdd")

matypeofsubstance <- read_csv("MAPrimarySubstanceofUseWhenEnteringTreatmentbyTown.csv",
                              col_types = "cccccccccccc")

toxdeath <- read_csv("MAProportionDecedentsWithRxHistorybyToxicologyScreen.csv",
         skip = 1,
         col_types = "cdccccccdc")

@@

```{r}
counties <- read_csv("zip_codes_states.csv",
                     col_types = "dddccc") %>%
  filter(state == "MA") %>%
  rename(County = county) %>%
  rename(Municipality = city)

madeathbycounty <- read_csv("MAAverageAnnualOpioidRelatedDeathRateper100,000People.csv",
                            col_types = "cdcdddc")

countypop <- read_csv("countypop.csv",
                      col_types = "cd") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)

@@

povertybycounty <- read_csv("PovertyByCounty.csv",
                            col_types = "cd") %>%
  rename(subregion = County) %>%
  mutate(subregion = tolower(subregion))
